{\Large Less than a week left, still without a}\\ Title

### 2014-07-25 sections/introduction.tex
add \url

For our case study, we used a review history of Gerrit\footnote{https://code.google.com/p/gerrit/} system which is tool for supporting MCR process. Our case studied project is Qt\footnote{http://qt-project.org/}, a open source project of a cross-platform application and UI framework supported by Digia corporation. To validate our approach, we manually classify the usefulness for 320 comments and measure its accuracy. We also used our predictive model for the all set of comments to preliminary estimate quality of reviews. According to this, we address the following two research questions:

>>>>

For our case study, we used a review history of Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system which is tool for supporting MCR process. Our case studied project is Qt\footnote{\url{http://qt-project.org/}}, a open source project of a cross-platform application and UI framework supported by Digia corporation. To validate our approach, we manually classify the usefulness for 320 comments and measure its accuracy. We also used our predictive model for the all set of comments to preliminary estimate quality of reviews. According to this, we address the following two research questions:
